\documentclass{report}

\begin{document}

\title{AI Acceleration and Biological Applications of Artificial Intelligence and Machine Learning}
\author{Stewart Nash}
\date{2026}

\maketitle

\begin{abstract}
This report investigates hardware acceleration of artificial intelligence and the application of artificial intelligence and machine learning
\end{abstract}

\tableofcontents

\chapter{AI Acceleration}

There are various platforms available using GPU compute to accelerate various scientific workloads.
\begin{itemize}
	\item CUDA
	\item ZLUDA
	\item oneAPI
	\item ROCm
		\begin{itemize}
			\item HIP
		\end{itemize}
	\item OpenCL
	\item SYCL
	\item Vulkan
\end{itemize}

We will look at CUDA. Our primary interest is in SYCL and Intel oneAPI for Intel GPUs. Secondarily, we will look at AMDs ROCm and HIP. We will look at the graphics pipeline and ask how both OpenGL and Vulkan might be leveraged as an alternative to these acceleration libraries.

\section{oneAPI}

OneAPI is an open standard for unified API for accelerators.

\section{ROCm}

ROCm is a software stack (produced by AMD) for GPU programming.

\section{OpenCL}

OpenCL is a framework for creating programs across different platforms. OpenCL specifies both a programming language and an API.

\section{SYCL}

SYCL is a programming model based on C++17.

\section{Vulkan}

Vulkan is a cross-platform API offering an open standard for 3D graphics.

\chapter{Protein Folding}

A neural network will be genertaed that can predict protein folding given a sequence of amino acids similar to AlphaFold. Also a neural network will be generated which can create de novo proteins such as RFdiffusion. The goal in this case would be to create a protein with a specified binding site.

AlphaFold is a neural network which is able to predict protein folding with variable accuracy. AlphaFold was trained on the content of PDB. AlphaFold uses a transformer architecture.

\chapter{Gene Splicing}

Splicing is the transformation of pre-mRNA into mRNA by the removal of introns. A deep-learning model similar to SpliceAI will be constructed to predict introns. This will be part of a larger suite of tools which identify numerous genetic sequences. Ideally the library will identify all known regulatory elements of transcription in both human and mice. This will be a complete computer of genetic expression in a library that can recreate the transcriptome.

\end{document}


